Temperature Measurements in Optical Tweezer Experiments

### 2016-08-23 doc/draft1.tex
changes changes changes

\subsection{Reduced Units}
\subsection{The Glass Nanoparticle}
The glass particle from the experiment will be represented by a system of particles, interacting via a Lennard-Jones potential of the form
\begin{equation}
    U(r) = 4\varepsilon\left[\left(\frac\sigma r\right)^{12} - \left(\frac\sigma r\right)^6\right]
\end{equation}
or, using reduced units:
\begin{equation}
    U(r^*) = 4\left[{r^*}^{-12} - {r^*}^{-6}\right]
\end{equation}

>>>>

\subsection{The Glass Nanoparticle}
The glass particle from the experiment will be represented by a system of 864 particles, aligned regularly on a FCC (face centered cubic) lattice.
This alignment is achieved by defining a minimum cell, containing points:
\begin{eqnarray*}
    p_1 &=& \{0,0,0\}\\
    p_2 &=& \{0.5,0.5,0\}\\
    p_3 &=& \{0.5,0,0.5\}\\
    p_4 &=& \{0,0.5,0.5\}
\end{eqnarray*}
The whole system is then  created by copying this unit cell.\\
The interaction between the atoms is modeled by the Lennard-Jones potential. It has the form
\begin{equation}
    U(r) = 4\varepsilon\left[\left(\frac\sigma r\right)^{12} - \left(\frac\sigma r\right)^6\right].
\end{equation}
To simplify the equation and computation of the potential and other quantities, like the forces or pressure, it is useful to introduce reduced units.
In general, reduced units BLABLABLA THINK OF GOOD TEXT HEREJKA\\
The basic units in a system with Lennard-Jones interaction are length ($\sigma$), energy ($\varepsilon$ or $\varepsilon / k_B$) and mass ($m$). Every 
quantity can now be written in terms of this units, so they become reduced quantities, denotet by an asterisk. The most important ones are:
\begin{eqnarray*}
    r^* &=& r/\sigma\\
    T^* &=& k_B/\varepsilon \ T\\
    U^* &=& U/\varepsilon \\
    P^* &=& P \sigma^3/\varepsilon 
\end{eqnarray*}
With the above introduced reduced units, the Lennard-Jones potential can be written as
\begin{equation}
    U(r^*) = 4\left[{r^*}^{-12} - {r^*}^{-6}\right].
\end{equation}
Since this is the most practical form, it will be used without the asterisk from here on.\\
The Lennard-Jones potential is an additive pair-potential, so the total energy of the system can be calculated by summing over all pairs of atoms:
\begin{equation}
    U_{\text{tot}} = \sum_{i=1}^{N-1}\sum_{j=i+1}^N4\left[{r_{ij}}^{-12} - {r_{ij}}^{-6}\right]
\end{equation}
where $r_{ij}$ denotes the distance between atom $i$ and $j$. \\
The Velocity-Verlet algorithm uses the forces to calculate the positions and velocities for the next timestep, we need to calculate the derivative of
the potential energy:
\begin{eqnarray}
    F_{x} &=& -\frac{\partial}{\partial x} U(r) \nonumber\\
                &=& -\frac{\partial}{\partial x} 4\left[{r}^{-12} - {r}^{-6}\right] \nonumber\\
                &=& -4 \left[(-12){r}^{-13} - (-6){r}^{-7}\right] \frac{\partial r}{\partial x} \nonumber\\
                &=& 48 \left[r^{-13} - 0.5 \ r^{-7}\right] \frac{x}{r} \nonumber\\
    \label{eq:ljforce} &=& 48 \left[r^{-14} - 0.5 \ r^{-8}\right] x
\end{eqnarray}
This is the component of the force in x-direction -- the other components are calculated analogously.
